Media Matters/The Battle between Fake News and Fox News

### 2024-04-17 paper/paper.qmd
fix

---
title: "Media Matters/The Battle between Fake News and Fox News"
subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
author: 
  - Hannah Yu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-result highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings. These discussions address the voting prediction results based on TV types, party affiliation, and media influence, and discuss policy implications from the study.

@@

summary <- 
  ces2020 |>
  summary() |>
  kable()

# Convert the summary to a data frame
summary_df <- as.data.frame(summary)

# Print the summary using pander
pander(summary_df, style = "grid", split.tables = Inf)

```
@tbl-summary presents a summary of the cleaned data, showing detailed statistics about the dataset. It is evident that Biden has more supporters in this election. The seven listed media networks capture the majority of networks people watch; while `Other` captures the rest. Due to the conflict of "Local Newscast" with the variables for media use networks, the number of respondents that only watch local newscast becomes 0 after cleaning. If the respondent only watches local newscasts, then they would skip all the questions related to national newscasts (e.g. Do you watch ABC?) since these questions are not applicable. With no further media-related information for voters who only watch local newscasts, this value is excluded from later examinations and modelling. There are more respondents identifying as Democrats than any other party. There are almost equal amount of Republicans and Independent voters, and only 534 voters identified as "Other."

@@

# Model {@sec-model}

@@

# Results {@sec-results}

@@

{
  print(
    ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
      geom_bar() +
      facet_wrap(facets = vars(Party)) +
      labs(
        title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
        x = "TV Type",
        y = "Count",
        color = "Voted for Biden (1) or Trump (0)"
      ) +
      scale_fill_brewer(palette = "Set1") +
      theme_minimal()
  )
}

>>>>

---
title: "Media Matters/The Battle between Fake News and Fox News"
subtitle: "Exploring the Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Voters from Different Parties"
author: 
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

The remainder of this paper is structured as follows: @sec-data demonstrates the data used for this paper, @sec-model builds the model and discusses its justification and explanation, @sec-results highlights the results of the predictions using tables and graphs, and @sec-discussion contains discussions conducted based on the findings. These discussions address the voting prediction results based on TV types, party affiliation, and media influence, and discuss policy implications from the study.

@@

ces2020 %>%
  select(1:6) %>%
  summary() %>%
  kable() %>%
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

```
```{r}
#| message: false
#| echo: false
#| warning: false

ces2020 %>%
  select(7:11) %>%
  summary() %>%
  kable() %>%
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

@tbl-summary presents a summary of the cleaned data, showing detailed statistics about the dataset. It is evident that Biden has more supporters in this election. The seven listed media networks capture the majority of networks people watch; while `Other` captures the rest. Due to the conflict of "Local Newscast" with the variables for media use networks, the number of respondents that only watch local newscast becomes 0 after cleaning. If the respondent only watches local newscasts, then they would skip all the questions related to national newscasts (e.g. Do you watch ABC?) since these questions are not applicable. With no further media-related information for voters who only watch local newscasts, this value is excluded from later examinations and modelling. There are more respondents identifying as Democrats than any other party. There are almost equal amount of Republicans and Independent voters, and only 534 voters identified as "Other."

@@

# Model {#sec-model}

@@

# Results {#sec-results}

@@

{
  print(
    ggplot(ces2020, aes(x = TV_type, fill = voted_for)) +
      geom_bar() +
      facet_wrap(facets = vars(Party)) +
      labs(
        title = "Relationship Between TV News Consumption and Voting Behaviour by Party",
        x = "TV Type",
        y = "Count",
        color = "Voted for Biden (1) or Trump (0)"
      ) +
      scale_fill_brewer(palette = "Set1")   )
}
